Modelling BCG vaccination in the UK

### 2019-12-11 rmds/10-model-results.Rmd
complete dodd typos

This chapter details the approach used to extrapolate the findings from the previous chapter beyond the change in BCG policy in 2005 and into the future. It first outlines the scenarios considered, then details the assumptions used to expand the time horizon of the model. Finally the impact of each scenario is explored over multiple time horizons. As discussed in the previous chapter these findings are preliminary in nature, meaning quantitative conclusions cannot be drawn and qualitative conclusions must be appropriately caveat-ed.

@@

```{r 10-table-future-incidence}
sum_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CI)")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "Forecast of overall TB incidence for each scenario evaluated from 2005 to 2040.", 
  caption = "Forecast of overall TB incidence for each scenario evaluated from 2005 to 2040. For brevity only 5 year intervals are shown. (95\\% CI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r 10-table-deaths-preds}
sum_deaths_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CI)")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "Forecast of overall TB mortality for each scenario evaluated from 2005 to 2040.", 
  caption = "Forecast of overall TB mortality for each scenario evaluated from 2005 to 2040. For brevity only 5 year intervals are shown.(95\\% CI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

>>>>

This chapter details the approach used to extrapolate the findings from the previous chapter beyond the change in BCG policy in 2005 and into the future. It first outlines the scenarios considered, then details the assumptions used to expand the time horizon of the model. Finally the impact of each scenario is explored over multiple time horizons. As discussed in the previous chapter these findings are preliminary in nature, meaning quantitative conclusions cannot be drawn and qualitative conclusions must be appropriately caveated.

@@

```{r 10-table-future-incidence}
sum_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CrI)")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "Forecast of overall TB incidence for each scenario evaluated from 2005 to 2040.", 
  caption = "Forecast of overall TB incidence for each scenario evaluated from 2005 to 2040. For brevity only 5 year intervals are shown. (95\\% CrI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r 10-table-deaths-preds}
sum_deaths_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CrI)")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "Forecast of overall TB mortality for each scenario evaluated from 2005 to 2040.", 
  caption = "Forecast of overall TB mortality for each scenario evaluated from 2005 to 2040. For brevity only 5 year intervals are shown.(95\\% CrI): 95\\% credible interval estimated using the 2.5\\% quantile and the 97.5\\% quantile.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```
